Case study validations of automatic bullet matching

### 2018-11-27 index.Rmd
fix table... again. Swear I fixed that before....

When evaluating algorithm performance, it is useful to systematically assess  the set of possible outcomes. If ground truth and the algorithm's prediction match, we have either a correct identification or a correct exclusion. If ground truth and the algorithm's prediction do not match, we distinguish between two types of errors, which we will refer to as \textbf{wrong identification} and \textbf{missed identification}. Wrong identifications are those in which two bullets from different sources are determined to be from the same source. Missed identifications are those in which two bullets from the same source are determined to be from different sources. The full range of possible outcomes is shown in \autoref{tab:possible-outcomes}. \hh{XXX I know that you have spent a ton of time on this table - but could you make it less tall? It's taking a ton of space. }
\begin{table}
\centering
\begin{tabular}{c|ccc}
\multicolumn{2}{c}{} & \multicolumn{2}{c}{\textbf{Ground Truth}}\\\cline{3-4}
\multicolumn{2}{c}{} & \multicolumn{1}{|c}{Same Source} & \multicolumn{1}{|c|}{Different Source} \\\cline{2-4}
\multirow{8}{*}{\rotatebox[origin=c]{90}{\hfill \textbf{Results}\hspace{5mm}\hfill}} & 
  \multirow{4}{*}{\rotatebox[origin=c]{90}{\hspace{1mm}Exclusion\hspace{1mm}}} & \multicolumn{1}{|c}{} & \multicolumn{1}{|c|}{}\\
  <!-- & &   \multicolumn{1}{|c}{} & \multicolumn{1}{|c|}{}\\ -->
  & &  \multicolumn{1}{|c}{Missed} & \multicolumn{1}{|c|}{Correct}\\
  & &  \multicolumn{1}{|c}{Identification} & \multicolumn{1}{|c|}{Exclusion}\\
  <!-- & &   \multicolumn{1}{|c}{} & \multicolumn{1}{|c|}{}\\ -->
  & &  \multicolumn{1}{|c}{} & \multicolumn{1}{|c|}{} \\\cline{2-4}
& \multirow{4}{*}{\rotatebox[origin=c]{90}{\hspace{1mm}Identification\hspace{1mm}}}  & \multicolumn{1}{|c}{} & \multicolumn{1}{|c|}{}\\
  <!-- & &  \multicolumn{1}{|c}{} & \multicolumn{1}{|c|}{}\\ -->
  & &  \multicolumn{1}{|c}{Correct} & \multicolumn{1}{|c|}{Wrong}\\
  & &  \multicolumn{1}{|c}{Identification} & \multicolumn{1}{|c|}{Identification}\\
  <!-- & &  \multicolumn{1}{|c}{} & \multicolumn{1}{|c|}{}\\ -->
  & &  \multicolumn{1}{|c}{} & \multicolumn{1}{|c|}{} \\\cline{2-4}
\end{tabular}
\caption{Possible outcomes of an examination of two pieces of evidence. Correct decisions are shown in the top-right and bottom-left corners; incorrect decisions in the top-left and bottom-right corners.\label{tab:possible-outcomes}}
\end{table}

>>>>

When evaluating algorithm performance, it is useful to systematically assess  the set of possible outcomes. If ground truth and the algorithm's prediction match, we have either a correct identification or a correct exclusion. If ground truth and the algorithm's prediction do not match, we distinguish between two types of errors, which we will refer to as \textbf{wrong identification} and \textbf{missed identification}. Wrong identifications are those in which two bullets from different sources are determined to be from the same source. Missed identifications are those in which two bullets from the same source are determined to be from different sources. The full range of possible outcomes is shown in \autoref{tab:possible-outcomes}. \hh{XXX I know that you have spent a ton of time on this table - but could you make it less tall? It's taking a ton of space. }
\begin{table}
\centering
\begin{tabular}{c|ccc}
\multicolumn{2}{c}{} & \multicolumn{2}{c}{\textbf{Ground Truth}}\\\cline{3-4}
\multicolumn{2}{c}{} & \multicolumn{1}{|c}{Same Source} & \multicolumn{1}{|c|}{Different Source} \\\cline{2-4}
\multirow{8}{*}{\rotatebox[origin=c]{90}{\hfill \textbf{Results}\hspace{5mm}\hfill}} & 
  \multirow{4}{*}{\rotatebox[origin=c]{90}{\hspace{1mm}Exclusion\hspace{1mm}}} & \multicolumn{1}{|c}{} & \multicolumn{1}{|c|}{}\\
  % & &   \multicolumn{1}{|c}{} & \multicolumn{1}{|c|}{}\\ 
  & &  \multicolumn{1}{|c}{Missed} & \multicolumn{1}{|c|}{Correct}\\
  & &  \multicolumn{1}{|c}{Identification} & \multicolumn{1}{|c|}{Exclusion}\\
  % & &   \multicolumn{1}{|c}{} & \multicolumn{1}{|c|}{}\\ 
  & &  \multicolumn{1}{|c}{} & \multicolumn{1}{|c|}{} \\\cline{2-4}
& \multirow{4}{*}{\rotatebox[origin=c]{90}{\hspace{1mm}Identification\hspace{1mm}}}  & \multicolumn{1}{|c}{} & \multicolumn{1}{|c|}{}\\
  % & &  \multicolumn{1}{|c}{} & \multicolumn{1}{|c|}{}\\ 
  & &  \multicolumn{1}{|c}{Correct} & \multicolumn{1}{|c|}{Wrong}\\
  & &  \multicolumn{1}{|c}{Identification} & \multicolumn{1}{|c|}{Identification}\\
  % & &  \multicolumn{1}{|c}{} & \multicolumn{1}{|c|}{}\\ 
  & &  \multicolumn{1}{|c}{} & \multicolumn{1}{|c|}{} \\\cline{2-4}
\end{tabular}
\caption{Possible outcomes of an examination of two pieces of evidence. Correct decisions are shown in the top-right and bottom-left corners; incorrect decisions in the top-left and bottom-right corners.\label{tab:possible-outcomes}}
\end{table}
